---
title: "Project name and project number"
subtitle: "SAP and/or study protocol version"
description: "bla bla"
author:
  - name: "Quarto Muster"
    orcid: 111
    email: "xxx@unibe.ch"
    affiliation: "Department of Clinical Research, University of Bern"
format: qmd-ctuhtml-html
bibliography: references.bib
---

# Methods

This section describes the methods used in the study. Quartones provides first evidence in @ref1. A general overview is provided in @ref2. References can be used over the bibtex bibliography.

## Methods subsection 1

## Study population

Insert here description of study population. Most likely a flowchart is necessary for describing eligibility of patients and for reproducibility.

```{r}
#| echo: false
#| results: hide
#| message: false
#| fig-height: 8
#| fig-width: 8

library(Gmisc)
library(grid)

grid.newpage()

N0 <- 100
N1 <- 75

x_coord1 <- 0.3

text_box1 <- paste0("Population 1\nN=", N0)
box1 <- boxGrob(text_box1, x=x_coord1, y=0.9, bjust = "center")
box1

text_box2 <- paste0("Population 2\nN=", N1)
box2 <- boxGrob(text_box2, x=x_coord1, y=0.1, bjust = "center")
box2

excluded1 <- boxGrob(paste0("Exclusion (n=", N0-N1, ")"), x = x_coord1+0.27, 
                     y = (coords(box2)$top + coords(box1)$bottom)/2, 
                     just="left", bjust = "left")
excluded1

connectGrob(box1, box2, "vertical")
connectGrob(box1, excluded1, "-")
```

## Statistical methods

Describe the methods, ideally in a form that can be used directly in a paper. Report the statistical software(s) used. 

## Results

### Results subsection 1

### Interactive descriptive tables

```{r}
#| echo: true
#| message: false
#| fig-height: 8
#| fig-width: 8

set.seed(1)
n <- 1000

a <- rnorm(n, mean=40, sd=20)
b <- rpois(n, lambda=3)
c <- rpois(n, lambda=1.5)

data <- data.frame(age=a, num_coffee=b, quarto=c)

library(tidyverse)
data_agg <- data %>% group_by(quarto) %>% 
  summarise(mean_age=round(mean(age),1), 
            sum_coffee=sum(num_coffee))

library(DT)
# Build factors for filtering in datatable()
data_agg$sum_coffee <- factor(data_agg$sum_coffee)
data_agg$quarto <- factor(data_agg$quarto)

col_names_table <- c("Intensity of Quarto use", 
                     "Mean age", "Sum of coffees")
datatable(data_agg, colnames=col_names_table, 
          rownames = F, filter = 'top', 
          options = list(pageLength = 20))
```

### Interactive graphs

```{r}
#| echo: true
#| message: false
#| fig-height: 8
#| fig-width: 8

library(plotly)

fig <- ggplot(data_agg, aes(x=quarto, y=sum_coffee))+geom_point()+
  ylab("Intensity of Quarto use")+xlab("Sum of coffees")+theme_bw()
ggplotly(fig)
```

# Revision history

| Release date| Summary of changes | Reason for change(s) |
| --- | --- | --- |
| Nov 2, 2022 | New report 2 | Not applicable |
| Nov 1, 2022 | New report 1 | Not applicable |

# Reproducibility

## Data export

This report is based on the file XXX from the RedCap data export on date XXX.

## Version control

DCR uses the SVN version control system. This report is based on revision XXX.

## Session info

```{r, echo=T, message=F}
#| echo: true
#| message: false

sessionInfo()
```
