---
title: "CTU project name and CTU project number"
subtitle: "SAP and/or study protocol version"
description: "Sample size calculation"
author:
  - name: "Quarto Muster"
    orcid: 111
    email: "xxx@ctu.unibe.ch"
    affiliation: "CTU Bern, University of Bern"
format: qmd-ctuhtml-html
bibliography: references.bib
---

# Study objective

## Primary objective

Describe study objective. The study objective will usually be defined
according to:

-   Patients: Which patients are included in the study?
-   Interventions: Which are the intervention groups?
-   Comparisons: Which are the control groups?
-   Outcome: Which is the primary outcome?

## Primary outcome

Description of primary outcome, including: 

- Type of data (binary, ordinal, continuous, count, time-to-event) 
- Time point of assessment
- In case of continuous outcomes, the measurement scale/units of measurements

## Hypothesis (if applicable)

-   Description of null and alternative hypothesis
-   Testing framework (e.g. superiority)

# Methods and assumptions

-   Allocation ratio,
-   Type I and II error rate,
-   Effect measure, e.g. relative risk, difference in means
-   Minimal clinically relevant difference between the groups (or
    non-inferiority margin),
-   Assumptions about any further parameter that is used, e.g. standard
    deviation for continuous outcomes, baseline proportion/rate for
    binary/survival outcomes.
-   Any corrections for dropouts or withdrawals (if applicable),
-   Method or test used for the sample size calculation,
-   Statistics software used (unless standard test/method is used)

```{r}
#| include: false
# do calculations here...
```

# Result of sample size calculation

-   Result, e.g. a table
-   Wording of sample size calculation for the study proposal/protocol



# Revision history

| Release date| Summary of changes | Reason for change(s) |
| --- | --- | --- |
| Nov 1, 2022 | Version report 1 | Not applicable |


# Session info
<details>
<summary>Click to expand</summary>

```{r, echo=T, message=F}
#| echo: true
#| message: false
sessionInfo()
```

</details>
